Diversity relationships for plants and frugivores

### 2024-06-03 code/L2/L2_3_TropicalAndes_divRelationships.Rmd
update input files

---
title: "Diversity relationships for plants and frugivores"
author: "Hazel J. Anderson"
project: "Plant-Frugivore Diversity"
collaborators: "Beth E. Gerstner, Phoebe L. Zarnetske"
overview: "This script compares taxonomic and functional diversity relationships for plants and frugivores for various spatial grains and combined diversity for each grain."
data input: "ADD"
data output: "ADD"
date: "2023-10-04"
output: html_document
---

# Set file paths
```{r}
data_path<-file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L2')
output_path<- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L2')
```

@@

# Read in Data
```{r}
plant_cellRichness_1km <- read.csv(file.path(output_path,"TropicalAndes_plantRichness_1km.csv"))
frugivore_cellRichness_1km <- read.csv(file.path(output_path,"TropicalAndes_frugivoreRichness_1km.csv"))

plant_cellRichness_5km <- read.csv(file.path(output_path,"TropicalAndes_plantRichness_5km.csv"))
frugivore_cellRichness_5km <- read.csv(file.path(output_path,"TropicalAndes_frugivoreRichness_5km.csv"))

plant_cellRichness_10km <- read.csv(file.path(output_path,"TropicalAndes_plantRichness_10km.csv"))
frugivore_cellRichness_10km <- read.csv(file.path(output_path,"TropicalAndes_frugivoreRichness_10km.csv"))

plant_cellRichness_25km <- read.csv(file.path(output_path,"TropicalAndes_plantRichness_25km.csv"))
frugivore_cellRichness_25km <- read.csv(file.path(output_path,"TropicalAndes_frugivoreRichness_25km.csv"))

plant_cellRichness_50km <- read.csv(file.path(output_path,"TropicalAndes_plantRichness_50km.csv"))
frugivore_cellRichness_50km <- read.csv(file.path(output_path,"TropicalAndes_frugivoreRichness_50km.csv"))

plant_cellRichness_75km <- read.csv(file.path(output_path,"TropicalAndes_plantRichness_75km.csv"))
frugivore_cellRichness_75km <- read.csv(file.path(output_path,"TropicalAndes_frugivoreRichness_75km.csv"))

plant_cellRichness_100km <- read.csv(file.path(output_path,"TropicalAndes_plantRichness_100km.csv"))
frugivore_cellRichness_100km <- read.csv(file.path(output_path,"TropicalAndes_frugivoreRichness_100km.csv"))
```

>>>>

---
title: "Diversity relationships for plants and frugivores"
author: "Hazel J. Anderson"
project: "Plant-Frugivore Diversity"
collaborators: "Beth E. Gerstner, Phoebe L. Zarnetske"
overview: "This script compares taxonomic and functional diversity relationships for plants and frugivores for various spatial grains and combined diversity for each grain."
data input: "ADD"
data output: "ADD"
date: "2024-05-16"
output: html_document
---

# Set file paths
```{r}
data_path_L2 <-file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L2')
output_path <- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L2')
figure_path <- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/figures')
```

@@

# Read in Data
```{r}
plant_cellRichness_1km <- read.csv(file.path(data_path_L2,"TropicalAndes_plantRichness_1km.csv"))
frugivore_cellRichness_1km <- read.csv(file.path(data_path_L2,"TropicalAndes_frugivoreRichness_1km.csv"))

plant_cellRichness_5km <- read.csv(file.path(data_path_L2,"TropicalAndes_plantRichness_5km.csv"))
frugivore_cellRichness_5km <- read.csv(file.path(data_path_L2,"TropicalAndes_frugivoreRichness_5km.csv"))

plant_cellRichness_10km <- read.csv(file.path(data_path_L2,"TropicalAndes_plantRichness_10km.csv"))
frugivore_cellRichness_10km <- read.csv(file.path(data_path_L2,"TropicalAndes_frugivoreRichness_10km.csv"))

plant_cellRichness_25km <- read.csv(file.path(data_path_L2,"TropicalAndes_plantRichness_25km.csv"))
frugivore_cellRichness_25km <- read.csv(file.path(data_path_L2,"TropicalAndes_frugivoreRichness_25km.csv"))

plant_cellRichness_50km <- read.csv(file.path(data_path_L2,"TropicalAndes_plantRichness_50km.csv"))
frugivore_cellRichness_50km <- read.csv(file.path(data_path_L2,"TropicalAndes_frugivoreRichness_50km.csv"))

plant_cellRichness_75km <- read.csv(file.path(data_path_L2,"TropicalAndes_plantRichness_75km.csv"))
frugivore_cellRichness_75km <- read.csv(file.path(data_path_L2,"TropicalAndes_frugivoreRichness_75km.csv"))

plant_cellRichness_100km <- read.csv(file.path(data_path_L2,"TropicalAndes_plantRichness_100km.csv"))
frugivore_cellRichness_100km <- read.csv(file.path(data_path_L2,"TropicalAndes_frugivoreRichness_100km.csv"))
```
